---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# collector

draft for discussion

## Installation

Install with

```
pak::pak("cynkra/collector")
```


## Examples

`collector()` creates a new function, with an altered body but the same environment:

```{r}
library(collector)
add <- function(x, y) {
  x + y
}
environment(add) <- asNamespace("stats")
add2 <- collector(add)
add2
```

It behaves the same as the original but additionally it collects :

* The arguments
* The call
* The return value

```{r}
a <- 1
b <- 2
f <- function() add2(a, b)
f()
```

Note the use of `delayedAssign()` because arguments are not evaluated yet
at the start of the body, this is robust to functions that use NSE.

If we know we don't use NSE, we can use `force = TRUE`

```{r}
# if we 
add3 <- collector(add, force = TRUE)
add3(a, b)
```

Or we can choose

```{r}
# if we 
add4 <- collector(add, force = "x")
add4(a, b)
```

Results are collected in a list internally, which we can collect with the `journal()`
function :

```{r}
j <- journal()
j

as.list(j[1,])

as.list(j[2,])

as.list(j[3,])
```


